---
title: "Covid91 vaccine study Final2020"
author: "Jonathan Paul Clavio"
date: "Oct 27, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. The analysis of this new drug will be done across four target subgroups; gender, lgbtq, and the drug users.

$H_0$: The Null Hypothesis is that among the target population, the vaccine has no effect on whether they contract the virus or not.  

$H_A$: The Alternative Hypothesis is that among the target population, the vaccine has an effect on whether they contract the virus or not.  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

Every question is of a Cat~Cat type.

## Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

#### Female Graphical Results  

```{r}
dataf = filter(FinalData, sex=="gal")
barchartGC(~infected + treatment,data=dataf)
barchartGC(~infected + treatment,data=dataf, type="percent", main="Female")
```

Among the females who had COVID-19, It appears that those who had COVID-19 and took the drug, the vaccine does have an positive effect.  
  

#### Male Graphical Results  

```{r}
datag = filter(FinalData, sex=="guy")
barchartGC(~infected + treatment,data=datag)
barchartGC(~infected + treatment,data=datag, type="percent", main="Male")
```

Among the males who had COVID-19, it appears those who had took vaccine has a negative effect in that the males who take the vaccine will be more likely to get COVID-19.  


#### LGBTQ Graphical Results

```{r}
datal= filter(FinalData, LGBTQ=="gay")
barchartGC(~infected + treatment,data=datal)
barchartGC(~infected + treatment,data=datal, type="percent", main="LGBTQ")
```

Among the LGBTQ community who had COVID-19, it appears those who had took the vaccine has a negative effect in that those in the LGBTQ community who has taken it will be more likely to get COVID-19.  


### Drug User Graphical Results

```{r}
datad = filter(FinalData, DrugUser=="yes")
barchartGC(~infected + treatment,data=datag)
barchartGC(~infected + treatment,data=datag, type="percent", main="Drug User")
```

Among those who do drugs that also had COVID-19, it appears those who had took the vaccine has a negative effect in that they will be more likely to get COVID-19.  


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
